MSAD_PCA_Walkthrough

### 2017-01-25 Simulation_Vignette.Rmd
In processMonitor, we changed the n in the while() loop to be the total rows kept, rather than the rows kept after each iteration. I think this is the right thing to do, but I need to continue testing it. Further, I fixed the alarm_xts return. Previously it was only returning the alarmed observations from the last iteration of the while() loop. It now returns all the alarmed observations.
CURRENT ISSUE: we have an infectious off-by-one error in processMonitor. For three groups, the sum of the alarmed and non-alarmed observations is +6 over the total tested observations.

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).
